Optimal Parameter Selection in Markov State Models for Biomolecular Conformational Dynamics

### 2013-08-15 paper/paper2.tex
Added the missing shaw citation for ww data
tica citation

\begin{figure}
\centering
\includegraphics[width=3in]{figs/fig1_rbow.png}
\caption{Three systems studied in this work. (a) Langevin dynamics on the two dimensional M\"{u}ller potential. (b) 50 ns of dynamics of alanine dipeptide. (c) 200 $\mu s$ of dynamics of the Fip35 WW domain\cite{Liu2008Experimental}, courtesy of D.E. Shaw research \cite{}.}
\end{figure}

@@

To test the procedure on a larger protein system, we reanalyzed two ultra-long 100 $\mu s$ molecular dynamics trajectories of the Fip35 WW domain\cite{Liu2008Experimental}, provided courtesy of D.E. Shaw Research \cite{}. In order to reduce the dimensionality of the problem, especially critical for the computation of the state volumes, we first preprocess the trajectories using time-structure based independent components analysis, retaining between two and six uncorrelated(?) linear combination of pairwise distances(?).

>>>>

\begin{figure}
\centering
\includegraphics[width=3in]{figs/fig1_rbow.png}
\caption{Three systems studied in this work. (a) Langevin dynamics on the two dimensional M\"{u}ller potential. (b) 50 ns of dynamics of alanine dipeptide. (c) 200 $\mu s$ of dynamics of the Fip35 WW domain\cite{Liu2008Experimental}, courtesy of D.E. Shaw research \cite{Shaw2010Atomic}.}
\end{figure}

@@

To test the procedure on a larger protein system, we reanalyzed two ultra-long 100 $\mu s$ molecular dynamics trajectories of the Fip35 WW domain\cite{Liu2008Experimental}, provided courtesy of D.E. Shaw Research \cite{Shaw2010Atomic}. In order to reduce the dimensionality of the problem, especially critical for the computation of the state volumes, we first preprocess the trajectories using time-structure based independent components analysis\cite{Schwantes2013Improvements}, retaining between two and six uncorrelated(?) linear combination of pairwise distances(?).
